\LaTeXe\ guide for the Journal of Functional Programming

### 2019-04-28 papers/jfp/4-schedulers.tex
Answer questions in S4

This scheduler (when combined with a suitable rebuilder) provides a minimal
build system which supports dynamic dependencies. The difficulties are all
engineering in nature. To implement suspension there are two standard
approaches:

@@

\q{Andrey}{It's unclear how our \hs{busy} build system fits into the two above
approaches. It probably is a third approach (i.e. using stack), but it's
unsuitable for real build systems that call external processes. Shall we mention
this?}

\q{Andrey}{A follow-up to the above: our \Shake models use neither of the two
above approaches, which seems a bit unsatisfactory. Can we at least hint how
our models could be adapted to use the continuation-passing style? Can we write
\hs{busyCPS}?}

>>>>

This scheduler (when combined with a suitable rebuilder) provides a minimal
build system which supports dynamic dependencies. In our model, a suspending
scheduler easy to write -- it makes a function call to compute each dependency. However,
a more practical implementation is likely to build multiple dependencies in parallel,
which then requires a more explicit suspension and resumption. To implement
suspension there are two standard approaches:

@@
